A Possibilistic Valid-time Model

### 2011-12-12 trunk/ipmu2012/preliminaries.tex
Still not the final version!

This work will deal with ill-known intervals. These are ill-known sets, defined and represented via a start and end point, which will be ill-known values. The elements of the set are the values between the start and end point. An closed ill-known interval with start point $X$ and end point $Y$ is noted here $\left[X, Y\right]$. The correspondences and transitions between the representations of ill-known sets and between the representation of an ill-known set and an ill-known interval are part of the authors current research.

\subsection{\label{subsec:fuzzy-numbers}Fuzzy Numbers and Fuzzy Intervals}
Among others, Dubois and Prade~\cite{Dubois1983} use the following definition of a \emph{fuzzy interval}.
\begin{definition}
A fuzzy interval is a fuzzy set $M$, defined by a membership function $\mu_{M}$, on the set of real numbers $\mathbb{R}$ such that:
\begin{eqnarray}
\mu_{M} : & \!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\! \mathbb{R} \rightarrow \left[0,1\right] \nonumber \\ 
\forall (u,v)\in\mathbb{R}^2: \forall w \in [u,v]:&\mu_M(w) \geq\min(\mu_M(u),\mu_M(v))  \\
\exists m \in \mathbb{R} : & \!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\! \mu_M(m)=1 
\end{eqnarray}
\end{definition}
If this modal value $m$ is unique, then $M$ is referred to as a \emph{fuzzy number}. In other words, if the core of a fuzzy interval is a singleton, it is referred to as a fuzzy number.

A simple form of the membership function of a fuzzy interval is a trapezoidal function. It can be shown that such a membership function $\mu_T$ for a fuzzy interval $T$ is convex and normalized. Four reel values, denoted $\alpha$, $\beta$, $\gamma$ and $\delta$ suffice to represent a trapezoidal membership function of a fuzzy interval. In this work, a fuzzy interval defined as such will be noted as $\left[\alpha, \beta, \gamma, \delta\right]$. %The corresponding membership function definition for this $\mu_T$ is then given by:

@@

The most convenient form of the membership function of a fuzzy number is a triangular function. It can be shown that such a membership function $\mu_M$ for a fuzzy number $M$ is convex and normalized. Three reel values, denoted $a$, $b$ and $D$, suffice to represent a triangular membership function of a fuzzy number and in this work, a fuzzy number defined as such will be noted as $\left[D, a, b \right]$. Here:
\begin{itemize}
\item
$D$ denotes the single value in the core of $M$
\item
$D-a$ is then $\inf \{u \in \mathbb{R} : \mu_{M}(u) > 0\}$
\item
$D+b$ is then $\sup \{u \in \mathbb{R} : \mu_{M}(u) > 0\}$
\end{itemize}
%\begin{figure}[h!]
%  \centering
%  \input{./graphs/triangular.tex}
%  \caption{Triangular membership function.}
%  \label{fig:triangular}
%\end{figure}

@@

\begin{align}
\Pos(A\text{ satisfies }C) & = \min_{a \in A}\left(\sup_{(a,w) \in R}\pi_{V}(w))\right) \\
\Nec(A\text{ satisfies }C) & = \min_{a \in A}\left(\inf_{(a,w) \notin R} 1-\pi_{V}(w)\right)
\end{align}

@@

@@

The possibility and necessity of the set satisfying both constraints is then:

>>>>

This work will deal with ill-known intervals. These are ill-known sets, defined and represented via a start and end point, which will be ill-known values. The elements of the set are the values between the start and end point. A closed ill-known interval with start point defined by possibilistic variable $X$ and end point by possibilistic variable $Y$ is noted here $\left[X, Y\right]$. The correspondences and transitions between the representations of ill-known sets and between the representation of an ill-known set and an ill-known interval are part of the authors current research.

\subsection{\label{subsec:fuzzy-numbers}Fuzzy Numbers and Fuzzy Intervals}
Among others, Dubois and Prade~\cite{Dubois1983} use fuzzy sets\cite{zadeh65} to define a \emph{fuzzy interval}:
\begin{definition}
A fuzzy interval is a fuzzy set $M$, defined by a membership function $\mu_{M}$, on the set of real numbers $\mathbb{R}$ such that:
\begin{eqnarray}
\mu_{M} : & \!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\! \mathbb{R} \rightarrow \left[0,1\right] \nonumber \\ 
\forall (u,v)\in\mathbb{R}^2: \forall w \in [u,v]:&\mu_M(w) \geq\min(\mu_M(u),\mu_M(v))  \\
\exists m \in \mathbb{R} : & \!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\! \mu_M(m)=1 
\end{eqnarray}
\end{definition}
If this modal value $m$ is unique, then $M$ is referred to as a \emph{fuzzy number}. In other words, if the core of a fuzzy interval is a singleton, it is referred to as a fuzzy number.

%A simple form of the membership function of a fuzzy interval is a trapezoidal function. It can be shown that such a membership function $\mu_T$ for a fuzzy interval $T$ is convex and normalized. Four reel values, denoted $\alpha$, $\beta$, $\gamma$ and $\delta$ suffice to represent a trapezoidal membership function of a fuzzy interval. In this work, a fuzzy interval defined as such will be noted as $\left[\alpha, \beta, \gamma, \delta\right]$. %The corresponding membership function definition for this $\mu_T$ is then given by:

@@

The most convenient form of the membership function of a fuzzy number is a triangular function. It can be shown that such a membership function $\mu_M$ for a fuzzy number $M$ is convex and normalized. Three real values, denoted $a$, $b$ and $D$, suffice to represent a triangular membership function of a fuzzy number and in this work, a fuzzy number defined as such will be noted as $\left[D, a, b \right]$. Here:
\begin{itemize}
\item
$D$ denotes the single value in the core of $M$
\item
$D-a$ is then $\inf \{u \in \mathbb{R} : \mu_{M}(u) > 0\}$
\item
$D+b$ is then $\sup \{u \in \mathbb{R} : \mu_{M}(u) > 0\}$
\end{itemize}

The membership function of such a fuzzy number is then given by:

\vspace{-10pt}

\begin{align}
\mu_M : & \quad \mathbb{R} \rightarrow \left[0,1\right] \nonumber\\
 : & \quad x \rightarrow
\begin{cases}
0 & \mbox{ if } \left(x < D-a\right) \vee \left(x > D+b\right) \\
\frac{1}{a}\left[x-\left(D-a\right)\right] & \mbox{ if } \left(x \geq D-a\right) \wedge (x \leq D)  \\
-\frac{1}{b}\left[x-\left(D+b\right)\right] & \mbox{ if } \left(x \geq D\right) \wedge (x \leq D+b)
\end{cases}
\end{align}

%\begin{figure}[h!]
%  \centering
%  \input{./graphs/triangular.tex}
%  \caption{Triangular membership function.}
%  \label{fig:triangular}
%\end{figure}

@@

\vspace{-10pt}

\begin{align}
\Pos(A\text{ satisfies }C) & = \min_{a \in A}\left(\sup_{(a,w) \in R}\pi_{V}(w))\right) \label{ill-known-pos}\\
\Nec(A\text{ satisfies }C) & = \min_{a \in A}\left(\inf_{(a,w) \notin R} 1-\pi_{V}(w)\right) \label{ill-known-nec}
\end{align}

@@

\vspace{-10pt}

@@

To calculate possibility and necessity concerning a conjunction of constraints, the $\min$ operator is used. The possibility and necessity of the set satisfying both constraints is then:

\vspace{-10pt}
